Instructions for ACL 2023 Proceedings

### 2023-05-05 paper/paper.tex
Add Makefile for paper, reasonable file names, figure folder.

The Gaussian Mixture model is a probabilistic model that assumes that each cluster follows a Gaussian (or normal) distribution and estimates the weight of the density function for each cluster \cite{reynolds2009gaussian,5298967}. We assume that the sentence vectors of two distinct classes should achieve high accuracy with Gaussian Mixture if they are displayed in a Gaussian distribution in space and are separable from each other.

However, there is a potential limitation to using this method. The separability and accuracy score may be underestimated if two clusters are not normally distributed, as illustrated in Figure \ref{fig:cirle}.

\begin{figure}[htp]
    \centering
    \includegraphics[scale=0.4]{Circle.jpg}
    \caption{Cases that Gaussian Mixture Underestimate the Separability of Two Clusters}
    \label{fig:cirle}
\end{figure}

Our evaluation results show that out of 78 pairs of derivation classes, 7 pairs achieved an accuracy score above 90\%, 24 pairs above 80\%, and 47 pairs above 60\%, as depicted in Figure \ref{fig:GM}.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[scale=0.4]{GM.png}
    \caption{Accuracy of Measured Separability with Gaussian Mixture}
    \label{fig:GM}
\end{figure}

% \subsection{SBERT as a classifier}
% This section shows whether the sentence embeddings trained on our models can serve as a classifier and separate sentences in terms of labels.

% For each derivation sentence, we compute the distance from its seed. The resulting vector. It is assumed that a certain type of derivation from a seed shares some similarities. A good classifier is assumed to group the same derivation types. For example, (sentence vector - seed vector)sentences with future tense are supposed to group together.
% visualize the distance vecotors

@@

% Sentence embeddings trained with SBERT can serve as classifier for some labels. For instance, the embeddings can separate 'future','past' and 'simple sentence' as in Figure X
% However, it does not work for the rest of groups:

@@

% Whether the degree of transformation can be characterized by SBERT sentence embeddings. 
% It shows the generalization group achieved most correlation.
% The more generalized sentences are further from seed sentence. While less generalized sentences (sentence meaning closer to seed sentences) has shorter distance to seed sentences

\bibliography{anthology}
\bibliographystyle{acl_natbib}

>>>>

The Gaussian Mixture model is a probabilistic model that assumes that each
cluster follows a Gaussian (or normal) distribution and estimates the weight of
the density function for each cluster~\cite{reynolds2009gaussian,5298967}. We
assume that the sentence vectors of two distinct classes should achieve high
accuracy with Gaussian Mixture if they are displayed in a Gaussian distribution
in space and are separable from each other.

However, there is a potential limitation to using this method. The separability
and accuracy score may be underestimated if two clusters are not normally
distributed, as illustrated in Figure~\ref{fig:cirle}.

\begin{figure}[htp]
    \centering
    \includegraphics[scale=0.4]{figs/Circle.jpg}
    \caption{Cases that Gaussian Mixture Underestimate the Separability of Two
    Clusters}\label{fig:cirle}
\end{figure}

Our evaluation results show that out of 78 pairs of derivation classes, 7 pairs
achieved an accuracy score above 90\%, 24 pairs above 80\%, and 47 pairs above
60\%, as depicted in Figure~\ref{fig:GM}.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[scale=0.4]{figs/GM.png}
    \caption{Accuracy of Measured Separability with Gaussian
    Mixture}\label{fig:GM}
\end{figure}

% \subsection{SBERT as a classifier}
% This section shows whether the sentence embeddings trained on our models can
% serve as a classifier and separate sentences in terms of labels.

% For each derivation sentence, we compute the distance from its seed. The
% resulting vector. It is assumed that a certain type of derivation from a seed
% shares some similarities. A good classifier is assumed to group the same
% derivation types. For example, (sentence vector - seed vector)sentences with
% future tense are supposed to group together.
% visualize the distance vecotors

@@

% Sentence embeddings trained with SBERT can serve as classifier for some
% labels. For instance, the embeddings can separate 'future','past' and 'simple
% sentence' as in Figure X
% However, it does not work for the rest of groups:

@@

% Whether the degree of transformation can be characterized by SBERT sentence
% embeddings. It shows the generalization group achieved most correlation. The
% more generalized sentences are further from seed sentence. While less
% generalized sentences (sentence meaning closer to seed sentences) has shorter
% distance to seed sentences

\bibliography{bibliography}
\bibliographystyle{acl_natbib}
